Inferring probabilistic stellar rotation periods using Gaussian processes

### 2017-02-13 documents/ms.tex
changes to the prior discussion section

continuing to develop, listed as follows:.

@@

        periodicity become dubious.
        A more rigorous criterion (which also
        takes into account dependencies on $\Gamma$) is presented below.
        Provided
        \begin{equation}
        \frac{{{P^2}}}{{{l^2}{\Gamma ^2}}} < \frac{{4\pi }}{3},
        \end{equation}
        the QP covariance function will have at least one inflection point
        other than at $|x_i-x_j|=0$
        So $\frac{{{P^2}}}{{{l^2}{\Gamma ^2}}} = \frac{{4\pi }}{3}$
        corresponds to a critical point at which secondary maxima disappear,
        and the behaviour of the kernel becomes dominated by the SE term
        rather than the periodic term.
        For $\Gamma\sim\mathcal{O}(1)$, this translates into $l\gtrsim P/2$.
        In practice, satisfying this criterion doesn't absolutely guarantee
        that function draws will have clear evidence of periodicity, but it
        does give you a quantitative boundary between obviously periodic
        behaviour and not-so-obviously periodic behaviour.
        It also provides some justification for a more stringent criterion
        such as $l>P$, or $l>2P$ (ensure that functions
        evolve significantly over time-scales longer than 2 periods).}

>>>>

continuing to develop, listed as follows:

@@

        periodicity become dubious.}
        % A more rigorous criterion (which also
        % takes into account dependencies on $\Gamma$) is presented below.
        % Provided
        % the QP covariance function will have at least one inflection point
        % other than at $|x_i-x_j|=0$, so $\frac{{{P^2}}}{{{l^2}{\Gamma ^2}}} =
        % \frac{{4\pi }}{3}$
        % corresponds to a critical point at which secondary maxima disappear,
        % and the behaviour of the kernel becomes dominated by the SE term
        % rather than the periodic term.
        % For $\Gamma\sim\mathcal{O}(1)$, this translates into $l\gtrsim P/2$.
        % In practice, satisfying this criterion doesn't absolutely guarantee
        % that function draws will have clear evidence of periodicity, but it
        % does provide a quantitative boundary between obviously periodic
        % behaviour and not-so-obviously periodic behaviour.
        % It also provides some justification for a more stringent criterion
        % such as $l>P$, or $l>2P$ (ensure that functions
        % evolve significantly over time-scales longer than 2 periods).}
